Linear and Differential Cryptanalysis of DES

### 2009-01-30 talk/draft1.tex

\subsection{Differential Attack: 3-round DES}
\begin{frame}
Differential Attack idea ...

@@

\begin{frame}
Differentials for SBoxes ...

\begin{frame}
Differential characteristics for SBoxes ...

\begin{frame}
Piling up over 3 rounds ...

>>>>

\subsection{Differential Attack: 4-round DES}
\begin{frame}
Differential Attack Idea

Similar to the differential attack on SPN, here we care about the differential characteristics of the cipher. So, the basic idea is as follows

\begin{itemize}
\item{Construct the difference tables for the S-Boxes}
\item{Find the most probable difference pairs}
\item{Combine the pairs through all the rounds to get a higly probable differential characteristic until the penultimate round}
\item{Exploit this differential characteristic by chosing a number of pairs of pliantexts with the desired difference and undo the last round by guessing the keybits}
\item{If the initial choice of the input difference was smart, we will only need to guess a few keybits}
\item{The guess approving the differential characteristic with highest probability is correct}
\end{itemize}

@@

\begin{frame}
The chosen input difference:$\Delta P = 20 00 00 00 00 00 00 00$

Round 1 Differential

\[ \Delta P = 20 00 00 00 00 00 00 00 \rightarrow 20 00 00 00 00 00 00 00 = \Delta V_1 \]
Probability: $p_1 = 1$ as Feistel gives output difference $0$ for input $0$

Round 2 Differential

\[ \Delta U_2 = \Delta V_1 = 20 00 00 00 00 00 00 00 \rightarrow \]

this calculations and coding has not been completed yet ... will be done ...
\end{frame}

\begin{frame}
Differentials for SBoxes
